\chapter{Conclusions}
\label{chap:conclusions}
Several searches for invisibly decaying Higgs bosons using data from proton-proton collisions at the LHC, collected by the CMS detector, and their interpretations have been shown. The searches include the first invisibly decaying Higgs boson search carried out in the \ac{VBF} channel, which used promptly reconstructed data from CMS, and placed an observed (expected) limit on \BRinv of 0.65 (0.49) at 95\% \ac{CL}~\cite{Chatrchyan:2014tja}.

The searches also include an updated search for \ac{VBF} produced invisibly decaying Higgs bosons carried out using data collected using the so-called parked triggers. These parked triggers had looser thresholds than those used for the first search in this channel, increasing the sensitivity of the analysis. Taking advantage of this increased sensitivity required measurements of the trigger efficiency which accounted for correlations between the variables used, and also a full re-optimisation of the analysis selection. This re-optimisation included the addition of new variables to discriminate against \ac{QCD} backgrounds. The observed (expected) limit on \BRinv obtained from this analysis was 0.57 (0.40) at 95\% \ac{CL}~\cite{CMS-PAS-HIG-14-038}.

Combinations of these two searches with searches performed in other Higgs boson production channels were also presented. The prompt data search was combined with two searches in the ZH production channel where the \PZ boson decays either to leptons or b-quarks. The observed (expected) limit on \BRinv obtained from this combination was 0.58 (0.44) at 95\% \ac{CL}.

The search using data collected with the parked triggers was combined with the same two searches in the ZH production channel and a further search targeting \ac{ggH} production and VH production where the vector boson decays hadronically. The observed (expected) limit on \BRinv obtained from this combination was 0.36 (0.30) at 95\% \ac{CL}~\cite{CMS-PAS-HIG-15-012}. This was the first combination of invisible Higgs boson decay searches featuring analyses targeting the three highest cross-section Higgs boson production channels.

Interpretations of invisibly decaying Higgs boson searches as limits on several models models of beyond the \ac{SM} physics, which include dark matter, were also shown. Projections of the parameter space that the search for invisibly decaying Higgs bosons in the \ac{VBF} channel will be able to exclude at a centre-of-mass energy of 13 \TeV were shown for several values of integrated luminosity. For \ac{EFT} models new physics scales up to 5 \TeV were found to be accessible with the full LHC dataset. For simplified spin 0 mediator models mediator and dark matter masses of up to 1 \TeV were found to be accessible for dark matter couplings of order 1.

Finally, projections of the sensitivity of the \ac{VBF} channel invisibly decaying Higgs boson search in Run 2 were made for several values of integrated luminosity. It was found that providing systematic uncertainties can be controlled to the 1\% level, limits on \BRinv of 5\% should be possible with the full LHC dataset.
